Bow shocks, bow waves, and dust waves

### 2017-12-15 papers/Papers1234/sec-dust-bow-intro.tex
Make a start on writing up the different dust regimes

>>>>

\section{Different types of bow}
\label{sec:different-types-bow}

\begin{figure*}
  \includegraphics[width=\linewidth]{figs/zones-v-n-plane}
  \caption{Bow regimes of parameter space (\(v, n\)) of the external
    stream for main-sequence OB stars of different masses:
    (a)~\SI{10}{M_\odot}, (b)~\SI{20}{M_\odot}, (c)~\SI{40}{M_\odot}. }
  \label{fig:zones-v-n-plane}
\end{figure*}

We will mainly consider the canonical case of a bow around a star of
bolometric luminosity, \(L\), with a radiatively driven
wind,\footnote{In \S~\ref{sec:case-inside-out} we consider the case of
  an external luminous source.} which is immersed in an external
stream of gas and dust with density, \(\rho\), and velocity, \(v\).  The
size and shape of the bow is determined by a generalized balance of
pressure (or, equivalently, momentum) between internal and external
sources.  We assume that the stream is supersonic and super-alfvenic,
so that the external pressure is dominated by the ram pressure:
\(\rho v^2\).

\subsection{Imperfect coupling between gas and dust}
\label{sec:imperf-coupl-betw}

\begin{figure}
  \includegraphics[width=\linewidth]{figs/decouple-v-n-plane}
  \caption{As Fig.~\ref{fig:zones-v-n-plane}(a), but accounting for
    gas-grain decoupling with constant efficiency \(\xi = 0.07\). }
  \label{fig:decouple-v-n-plane}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{figs/decouple-v40-versus-n}
  \caption{Vertical cut through Fig.~\ref{fig:decouple-v-n-plane},
    showing bow radius and different regimes for a fixed inflow
    velocity of \SI{40}{km.s^{-1}}.}
  \label{fig:decouple-v40-versus-n}
\end{figure}

\subsection{The case of inside-out bows with external illumination}
\label{sec:case-inside-out}
